Community Detection in the Setting of Generalized Random Dot Product Graphs

### 2023-01-11 slides/slides.Rmd
fixed typo

$$\ell(z, \theta; A) = \sum_{i<j} \sum_{k, \ell} z_{ik} z_{j \ell} \Big(A_{ij} \log_{k \ell} + (1 - A_{ij}) \log(1 - \theta_{k \ell}) \Big)$$

@@

## Example: Karantaka Villages

@@

**Theorem** (KKT):  
Let $A \sim \MBM(\{\alpha_1, ..., \alpha_K\}, \{F, ..., F\}, \{g_1, ..., g_K\}; \rho_n)$ such that $F$ has support $[0, 1]$, and each $g_k(t) = g(t; p_k)$ is is a curve of order $R$ that does not self-intersect (for any $s \neq t$, $g_k(s) \neq g_k(t)$). 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then if $n \rho_n = \omega(\log^{4c} n)$, as $n \to \infty$, the estimates outputted by $K$-curves clustering are such that 
$$L(\hat{z}_1, ..., \hat{z}_n, \hat{g}_1, ..., \hat{g}_K; X) \stackrel{p}{\to} 0.$$

>>>>

$$\ell(z, \theta; A) = \sum_{i<j} \sum_{k, \ell} z_{ik} z_{j \ell} \Big(A_{ij} \log \theta_{k \ell} + (1 - A_{ij}) \log(1 - \theta_{k \ell}) \Big)$$

@@

## Example: Karantaka Villages (Banerjee et al., 2013)

@@

**Theorem** (KTT):  
Let $A \sim \MBM(\{\alpha_1, ..., \alpha_K\}, \{F, ..., F\}, \{g_1, ..., g_K\}; \rho_n)$ such that $F$ has support $[0, 1]$, and each $g_k(t) = g(t; p_k)$ is is a curve of order $R$ that does not self-intersect (for any $s \neq t$, $g_k(s) \neq g_k(t)$). 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then if $n \rho_n = \omega(\log^{4c} n)$, as $n \to \infty$, the estimates outputted by $K$-curves clustering are such that 
$$L(\hat{z}_1, ..., \hat{z}_n, \hat{g}_1, ..., \hat{g}_K; X) \stackrel{p}{\to} 0.$$
